Methodology for Assessing the State of the Practice for Domain X

### 2020-10-12 StateOfPractice/Methodology/Methodology.tex
updated Section 2 of Methodology

Questions from Olu's Research Proposal:

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What are the attitudes and actions of research software developers toward:
\begin{enumerate}
\item sustainability?
\item usability?
\item modifiability? \pmi{think about and possibly remove this one}
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

\wss{Rather than focus on sustainability and productivity, should we focus on
  usability and modifiability for the SOP exercise?  Our current questions and
  experiments focus more on these topics.}

Questions from Overall Research Project folder:

\begin{enumerate}
\item What principles, processes, methodologies and tools are used by existing
  open source SCS projects? \pmi{keep}
\item What are the pain points for developers working on SCS projects?  What
  aspects of the existing processes, methodologies and tools do they consider
  could potentially be improved? \pmi{keep}
\end{enumerate}

@@

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be updated based on feedback}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{In second review}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be edited based on feedback}
\item \emph{Domain Experts}: Review domain software list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be edited - add intro}
\item \emph{Domain Experts}: Vet domain analysis. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts}) 
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be edited based on feedback}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item With short list:
\begin{enumerate}
\item Survey developers (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: these experiments need to be completed - to be discussed at next meeting}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

>>>>

The following are research questions that we want to answer in order to assess the state of practice of research software in our chosen domain:

\begin{enumerate}
\item What artifacts do current software packages produce? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed in order to reduce obstacles?
\item What are the attitudes and actions of research software developers toward:
\begin{enumerate}
\item sustainability?
\item usability?
\item modifiability?
\end{enumerate} 
\item For a given domain of research software, what current projects provide the best examples of high quality software and documentation?
\end{enumerate}

@@

\begin{enumerate}
\item Start with the state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be updated based on feedback}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{In second review}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be edited based on feedback}
\item \emph{Domain Experts}: Review domain software list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be edited - add intro}
\item \emph{Domain Experts}: Vet domain analysis. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts}) 
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be edited based on feedback}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item With short list:
\begin{enumerate}
\item Survey developers (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: these experiments need to be completed - to be discussed at next meeting}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}
